---
title: "XML Credict Decision Engine"
author: "David Soto"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(dplyr)
library("XML")
library("methods")
library(plyr)

```



## wrapper java 
The decisions that we take with the decision engine in corporate risk are stored in an oracle database, we need a wrapper java class to donwload those files (BLOB files ) in XMLs files, 

```{java }

public class CreateFilesDlogiPRE {

String path ="D:\\repos\\isban\\dlogi\\input\\";

private  void createFiles()
    {
        Statement stmt = null;
        ConexionPREIG ora = new ConexionPREIG();
        Connection connection  = ora.getconnection();
   
        String query =    " SELECT * FROM DLOG_INFO  where TO_CHAR(H9900_TSINICIO,'YYYY-MM-DD')>'2017-03-01'  and               (LTRIM(RTRIM(DLOG_INFO.H9900_TIPOSUBSEG))='03') ";


        try {
            stmt = connection.createStatement();
            System.out.println("quering");
			ResultSet rs = stmt.executeQuery(query);


        int cont = 0;
       while (rs.next())
         {
         cont++;

        Clob h9900_outdata = rs.getClob("H9900_INDATA");         
		Clob h9900_outdata = rs.getClob("H9900_OUTDATA");  
        String h9900_codcaso = rs.getString("h9900_codcaso");
          
      System.out.println("generating file " + h9900_codcaso);
        InputStream in = h9900_outdata.getAsciiStream();
     OutputStream out = null;  
                try {
                    out = new FileOutputStream(path+""+  h9900_codcaso +"_index_"+cont+".xml");
                } catch (FileNotFoundException ex) {
                    Logger.getLogger(createFilesofMTBdescargasPRE.class.getName()).log(Level.SEVERE, null, ex);
                }
        byte[] buff = new byte[4096];  // how much of the blob to read/write at a time
        int len = 0;
                try {
                    while ((len = in.read(buff)) != -1) {
                        out.write(buff, 0, len);
                    }
                } catch (IOException ex) {
                    Logger.getLogger(createFilesofMTBdescargasPRE.class.getName()).log(Level.SEVERE, null, ex);
                }
         }



ora.close();

} catch (SQLException ex) {
            Logger.getLogger(CreateFilesDlogiPRE.class.getName()).log(Level.SEVERE, null, ex);
            ora.close();
}

}

```


#from XML to DAtaset
with the packages XMLs and methods we transform the XMLs into datasets

```{r }



# this function is to move some files 
  my.file.rename <- function(from, to) {
    todir <- dirname(to)
    if (!isTRUE(file.info(todir)$isdir)) dir.create(todir, recursive=TRUE)
    file.rename(from = from,  to = to)
}

setwd("D:/repos/isban/dlogi/code/")


df <- data.frame(stringsAsFactors=FALSE) 


file.names  <- list.files("../prod_Data/", pattern="*.xml", full.names=TRUE) 

for(i in 2:length(file.names) -1 )
  {
 
              tryCatch( # apparentely there are some XMLS that have some problems with the encoding, i will save them in a separate folder to take a look later
                   {
                     xml_data <- xmlToList(file.names[i])}
                    
              , warning = function(war) {      
                      print(paste("MY_WARNING:  ",file.names[i]))
                      my.file.rename(from = paste0("../prod_Data/" ,file.names[i]),  to = paste0("../faulty/" ,file.names[i]) )
              }, error = function(err) {   
              print(paste("MY_ERROR:  ",file.names[i]))
              my.file.rename(from = paste0("../prod_Data/" ,file.names[i]),  to = paste0("../faulty/" ,file.names[i]) )
              
              })
              

  # we take some atributes mainly regarding the exposure of the customer
  
  SCBUKApp <- xml_data[["SCBUKApp"]][[".attrs"]]
  Applicant <- xml_data[["SCBUKApp"]][["Applicant"]][[".attrs"]]
  a <- append (SCBUKApp,Applicant)
  record <-data.frame(lapply(a, type.convert), stringsAsFactors=FALSE)
  df <-rbind.fill(df, record )
}


saveRDS(df, file.path('../input/', "creditDecision.rds"))

```


#the dataset


```{r datasets}
df <- readRDS("../input/credictDecision.rds")

df <- select (df, APP_TYPE,SYSTEM_DECISION, TOT_UNSEC_EXP, FINAL_APP_WDV, TOTAL_EXP_AGGR_CHANGE, TOTAL_EXP_AGGR_EXIST,TOTAL_EXP_AGGR_PROPOS
              , TOTAL_EXP_AGG_PROP_LT, TOTAL_EXP_NON_AGGR_CH, TOTAL_EXP_NON_AGGR_EX,  TOTAL_EXP_NON_AGGR_PR,   TOTAL_EXP_NON_AGG_PROP_LT,   LTV__PCT    )

dim(df) #- we will work with 7416 cases from the las 90 days
summary(df)

```




```{r include=FALSE, cache=FALSE}
library(xgboost)
library(Matrix)
library(vcd)

```

#xgboost

lets use xgboost to figure out which input variables have more importance  
what are the variables with more importance in this decision (80)  - "APPROVE" ? 

```{r APPROVE}

sparse_matrix <- sparse.model.matrix(SYSTEM_DECISION~.-1, data = df)


output_vector = df[,"SYSTEM_DECISION"] == "80"

bst <- xgboost(data = sparse_matrix, label = output_vector, max_depth = 4,
               eta = 1, nthread = 2, nrounds = 10,objective = "binary:logistic")

importance <- xgb.importance(feature_names = colnames(sparse_matrix), model = bst)
xgb.plot.importance(importance_matrix = importance)


```



# REFER_TO_UNDERWRITER
what are the variables with more importance in this decision decision (40)  - "REFER TO UNDERWRITER" ? 




```{r REFER_TO_UNDERWRITER}



sparse_matrix <- sparse.model.matrix(SYSTEM_DECISION~.-1, data = df)

output_vector = df[,"SYSTEM_DECISION"] == "40"

bst <- xgboost(data = sparse_matrix, label = output_vector, max_depth = 4,
               eta = 1, nthread = 2, nrounds = 10,objective = "binary:logistic")

importance <- xgb.importance(feature_names = colnames(sparse_matrix), model = bst)
xgb.plot.importance(importance_matrix = importance)


```




#FURTHER_INFO

what are the variables with more importance in this decision (40)  - "FURTHER INFO" ? 
```{r FURTHER_INFO}




sparse_matrix <- sparse.model.matrix(SYSTEM_DECISION~.-1, data = df)


output_vector = df[,"SYSTEM_DECISION"] == "110"

bst <- xgboost(data = sparse_matrix, label = output_vector, max_depth = 4,
               eta = 1, nthread = 2, nrounds = 10,objective = "binary:logistic")

importance <- xgb.importance(feature_names = colnames(sparse_matrix), model = bst)
xgb.plot.importance(importance_matrix = importance)

head(importance)
```



