---
title: "fidelity Prices"
author: "david soto"
date: "11/17/2017"
output: html_document
---

```{r setup, echo=T, include=T, message=F, warning=F}

rm(list = ls())
library(jsonlite)  
library(XML)       
library(RCurl)     
library(stringr)   
library(plyr)      
library(dplyr)     
library(lubridate) 

```

[you can check just the code here ](https://github.com/DavidMSoto/blog/blob/master/mfunds/code/ScrapingFidelity.R)

Recently Fidelity changed their website offering new products, 
basically we have about 101 ETFs, 89 IETFs and about 2800 mutual funds

Below are the urls to gatter this information throught JSON and convert them to datasets, 
The urls can look a little odd I got them using the web developer tools of mozilla, 
just take a look to the network console and you will see all the get /post/ put .. etc that the new 

What I really like about R, is the simpliclity of the code, look how we create 2 datasets with all the ETFs and investments funds.

![look how easy is to create the datasets using JSONs](http://www.fillmurray.com/600/400)



# System to have a little database with historical prices of the fidelity etfs

this entry is going to develop a very easy sistem to have all the historical data of all the fidelity products, 

 gather the products using a get operation from the morningstarg API
```{java  eim}
eim <- getProducts () ** etfs, investmentfs funds, mutual funds. 
eim <- datamungin(eim)
savefile (eim.Date) 
```

gather 5 years of  historical prices from financial times 
```{java  hp}
historical.prices <-gethistoricalpricesft(products,60)
savefile (historical.prices.date)
```

gather 1 month  of  historical prices from financial times 
```{java  ip}
infremental.prices <-gethistoricalpricesft(products,1)
savefile (historical.prices.date)
```

merge historical and incremental files  
```{java  u}
historical.prices.today <- infremental.prices.today Union historical.prices.date
```


#gather the Funds using a get operation from the morningstarg API

Funds allow investors to pool their money together, which a fund manager will then invest on their behalf. The manager is responsible for choosing investments for the fund and tries to grow investors' money by spreading it over a range of company shares, bonds etc.
Unit trusts, offshore funds and open-ended investment companies (OEICs) can all be referred to generically as funds.


```{r funds}


url_MFEI <-  "http://lt.morningstar.com/api/rest.svc/9vehuxllxs/security/screener?page=1&pageSize=3000&sortOrder=LegalName%20asc&outputType=json&version=1&languageId=en-GB&currencyId=GBP&universeIds=FOGBR%24%24ALL_3521&securityDataPoints=SecId%7CName%7CTenforeId%7CholdingTypeId%7Cisin%7Csedol%7CCustomAttributes1%7CCustomAttributes2%7CCustomExternalURL1%7CCustomExternalURL2%7CCustomExternalURL3%7CCustomIsClosed%7CCustomIsFavourite%7CCustomIsRecommended%7CQR_MonthDate%7CLegalName%7CCustomBuyFee%7CYield_M12%7COngoingCharge%7CCustomCategoryId3Name%7CStarRatingM255%7CQR_GBRReturnM12_5%7CQR_GBRReturnM12_4%7CQR_GBRReturnM12_3%7CQR_GBRReturnM12_2%7CQR_GBRReturnM12_1%7CCustomMinimumPurchaseAmount%7CCustomValue2%7CCustomAdditionalBuyFee%7CCustomSellFee%7CGBRReturnM0%7CGBRReturnM12%7CGBRReturnM36%7CGBRReturnM60%7CGBRReturnM120&filters=&term=&subUniverseId=MFEI"

MFEI <-getURL(url_MFEI) %>% fromJSON()  %>% as.data.frame



names(MFEI) <- gsub("rows.", "", names(MFEI)) # nicer names

MFEI$kind <- ifelse(  grepl("Acc",MFEI$LegalName),"Acc", "Inc") # we create a variable that says if is acc or icc


```


Exchange Traded Funds (ETFs)
Exchange traded funds are similar to the funds mentioned above except that they act like a share themselves, and are openly traded on a stock exchange such as the FTSE All Share.  Most ETFs aim to perform in line with a specific index or commodity (like gold) and often have low management fees.

Investment Trusts
These are funds registered as public limited companies (PLCs) with their own management teams and boards of directors. They can invest in public and private companies, have a specific number of shares in issue and are traded on a stock exchange themselves.


```{r fidelityJSONScraping }

url_ETFEI <- "http://lt.morningstar.com/api/rest.svc/9vehuxllxs/security/screener?page=1&pageSize=1000&sortOrder=LegalName%20asc&outputType=json&version=1&languageId=en-GB&currencyId=GBP&universeIds=ETEXG$XLON_3518|ETALL$$ALL_3518&securityDataPoints=SecId|Name|TenforeId|holdingTypeId|isin|sedol|QR_MonthDate|LegalName|Yield_M12|OngoingCharge|StarRatingM255|CustomCategoryId3Name|CollectedSRRI|QR_GBRReturnM12_5|QR_GBRReturnM12_4|QR_GBRReturnM12_3|QR_GBRReturnM12_2|QR_GBRReturnM12_1|CustomMinimumPurchaseAmount|GBRReturnM0|GBRReturnM12|GBRReturnM36|GBRReturnM60|GBRReturnM120&subUniverseId=ETFEI"

url_ITEI <-  "http://lt.morningstar.com/api/rest.svc/9vehuxllxs/security/screener?page=1&pageSize=1000&sortOrder=LegalName%20asc&outputType=json&version=1&languageId=en-GB&currencyId=GBP&universeIds=FCGBR%24%24ALL_3519&securityDataPoints=SecId%7CName%7CTenforeId%7CholdingTypeId%7Cisin%7Csedol%7CQR_MonthDate%7CLegalName%7CYield_M12%7CAnnualReportOngoingCharge%7CStarRatingM255%7CCustomCategoryId3Name%7CQR_GBRReturnM12_5%7CQR_GBRReturnM12_4%7CQR_GBRReturnM12_3%7CQR_GBRReturnM12_2%7CQR_GBRReturnM12_1%7CCustomMinimumPurchaseAmount%7CGBRReturnM0%7CGBRReturnM12%7CGBRReturnM36%7CGBRReturnM60%7CGBRReturnM120&filters=&term=&subUniverseId=ITEI"


ETFEI <- getURL(url_ETFEI) %>% fromJSON()  %>% as.data.frame
ITEI<- getURL(url_ITEI) %>% fromJSON()  %>% as.data.frame 


names(ETFEI) <- gsub("rows.", "", names(ETFEI)) # nicer names
names(ITEI) <- gsub("rows.", "", names(ITEI)) # nicer names

names(ITEI)[14] <- "OngoingCharge" #  change AnnualReportOngoingCharge for OngoingCharge

ei<- rbind.fill(ETFEI, ITEI)
eim <- rbind.fill(ei, MFEI)
```

# save 
```{r save , include=F}

saveRDS(eim, file.path(getwd(), "../input/eim.20171117.rds"))

```