---
title: "fidelity Prices"
author: "david soto"
date: "11/17/2017"
output: html_document
---


```{r setup, echo=T, include=T, message=F, warning=F}
rm(list = ls())

library(jsonlite)  
library(XML)       
library(RCurl)     
library(stringr)   
library(plyr)      
library(dplyr)     
library(lubridate) 

```



## Getting market data 

Apparently there is no good source of historical data for such  products as mutual funds,
I mean, there is no API to gather the historical data from yahoo finance or google finance for mutual funds or investments funds.
sometimeS if you want something good you have to make it yourself. 

With the fuction getFinancialtimesHistoricalData we gather the historical data from  Financial times, again we use a GET operation that gather a JSON

i am measuring the time for this operation because it takes a while, probably there is something that can be improved, feel free to commets the code. 

as you can see, gatering almost 200 products with a depth of two months we take ... 


```{r getFinancialtimesHistoricalData, echo=T}


getFinancialtimesHistoricalData <-function(products,months) {
  
  df.return <- data.frame(stringsAsFactors=FALSE) 
  start.time <- Sys.time() # let's see how much time we are going to spend in this 
  
  
  url.ft.base <- paste0("https://markets.ft.com/data/equities/ajax/get-historical-prices?startDate=", 
                        gsub("-", "/", Sys.Date()-months(months)) , "&endDate=", 
                        gsub("-", "/", Sys.Date()) , "&symbol=" )
  
  for (i in 1:nrow(products)){
    url.ft = paste0(url.ft.base,products[i,"isin"]) # 
    ft.xml <- getURL(url.ft) %>% fromJSON() %>%  htmlParse(asText = TRUE) 
    
    xmltop = xmlRoot(ft.xml) #gives content of root
    ft.df =ldply(xmlToList(xmltop[[1]]), data.frame) 
    
    if (nrow(ft.df) > 2 ) # not all the products have data in financial times, 
    {
      
      ft.df <- ft.df [-1,c(5,8,9,10,11,12)] # select the columns we need and remove the first row
      names(ft.df )<-c("date","Open","High","Low","Close","Volumen") # rename de columms
      
      ft.df<-merge(ft.df,products [i,] )
      
      df.return <-rbind( df.return ,ft.df )
      
    } else {   print( paste0( "the product", products[i,"isin"], "Does not have any data in financial times API")) }
    
  }
  
  print( Sys.time() - start.time)
  
  return(df.return)
  
}


```




#save

```{r save, echo=T}

eim <- readRDS("~/dataScience/blog/mfunds/input/eim20171117.rds")  
dfe<-getFinancialtimesHistoricalData(eim,60)
saveRDS( dfe, file.path(getwd(), "../input/historical.prices.date.rds") )

```


bola extra

```{java union, echo=T}

eim <- readRDS("~/dataScience/blog/mfunds/input/eim20171117.rds")  
dfe <-getFinancialtimesHistoricalData (eim,1) 

alldata <- readRDS("./input/etfs_20171108.rds")


library(sqldf)


trainf <- sqldf("SELECT * from dfe
                  UNION
                SELECT * from alldata
                ORDER BY Date
                 " )
```

