


---
title: "Investing with fidelity and R part I"
output: html_document
---

```{r setup, echo=T, include=T, message=F, warning=F}
rm(list = ls())

knitr::opts_chunk$set(echo = TRUE)

library(jsonlite)  
library(XML)       
library(RCurl)     
library(stringr)   
library(plyr)      
library(dplyr)     
library(lubridate) 

```


# Getting Etfs and investments funds from fidelity

Recently Fidelity changed their website offering new products, 
basically we have about 101 ETFs, 89 IETFs and about 2800 mutual funds

Below are the urls to gatter this information throught JSON and convert them to datasets, 
The urls can look a little odd I got them using the web developer tools of mozilla, 
just take a look to the network console and you will see all the get /post/ put .. etc that the new 

What I really like about R, is the simpliclity of the code, look how we create 2 datasets with all the ETFs and investments funds.




```{r fidelityJSONScraping }


url_ETFEI <- "http://lt.morningstar.com/api/rest.svc/9vehuxllxs/security/screener?page=1&pageSize=1000&sortOrder=LegalName%20asc&outputType=json&version=1&languageId=en-GB&currencyId=GBP&universeIds=ETEXG$XLON_3518|ETALL$$ALL_3518&securityDataPoints=SecId|Name|TenforeId|holdingTypeId|isin|sedol|QR_MonthDate|LegalName|Yield_M12|OngoingCharge|StarRatingM255|CustomCategoryId3Name|CollectedSRRI|QR_GBRReturnM12_5|QR_GBRReturnM12_4|QR_GBRReturnM12_3|QR_GBRReturnM12_2|QR_GBRReturnM12_1|CustomMinimumPurchaseAmount|GBRReturnM0|GBRReturnM12|GBRReturnM36|GBRReturnM60|GBRReturnM120&subUniverseId=ETFEI"

url_ITEI <-  "http://lt.morningstar.com/api/rest.svc/9vehuxllxs/security/screener?page=1&pageSize=1000&sortOrder=LegalName%20asc&outputType=json&version=1&languageId=en-GB&currencyId=GBP&universeIds=FCGBR%24%24ALL_3519&securityDataPoints=SecId%7CName%7CTenforeId%7CholdingTypeId%7Cisin%7Csedol%7CQR_MonthDate%7CLegalName%7CYield_M12%7CAnnualReportOngoingCharge%7CStarRatingM255%7CCustomCategoryId3Name%7CQR_GBRReturnM12_5%7CQR_GBRReturnM12_4%7CQR_GBRReturnM12_3%7CQR_GBRReturnM12_2%7CQR_GBRReturnM12_1%7CCustomMinimumPurchaseAmount%7CGBRReturnM0%7CGBRReturnM12%7CGBRReturnM36%7CGBRReturnM60%7CGBRReturnM120&filters=&term=&subUniverseId=ITEI"



ETFEI <- getURL(url_ETFEI) %>% fromJSON()  %>% as.data.frame
ITEI<- getURL(url_ITEI) %>% fromJSON()  %>% as.data.frame



#althougt the json gather many fields for this example we just use the below columns
ETFEI <- select (ETFEI,1,6,9,12,14,21)
ITEI <- select (ITEI,1,6,9,12,14,16)


names(ETFEI) <- c("type", "Name", "isin" , "LegalName", "OngoingCharge" , "category")
names(ITEI) <- c("type", "Name", "isin" , "LegalName", "OngoingCharge" , "category")


head(select (ITEI,2, 3))


```

## getting market data 

Apparently there is no good source of historical data for such  products as mutual funds,
I mean, there is no API to gather the historical data from yahoo finance or google finance for mutual funds or investments funds.
sometimeS if you want something good you have to make it yourself. 

With the fuction getFinancialtimesHistoricalData we gather the historical data from  Financial times, again we use a GET operation that gather a JSON

i am measuring the time for this operation because it takes a while, probably there is something that can be improved, feel free to commets the code. 

as you can see, gatering almost 200 products with a depth of two months we take ... 


```{r pressure, echo=T}


getFinancialtimesHistoricalData <-function(products,months) {

df.return <- data.frame(stringsAsFactors=FALSE) 
start.time <- Sys.time() # let's see how much time we are goint to spend in this 


url_ft_base <- paste0("https://markets.ft.com/data/equities/ajax/get-historical-prices?startDate=", 
                      gsub("-", "/", Sys.Date()-months(months)) , "&endDate=", 
                      gsub("-", "/", Sys.Date()) , "&symbol=" )

#for (i in 1:nrow(products)){
for (i in 1:5){
  
  url_ft = paste0(url_ft_base,products[i,3]) # third column is sthe isnn
  ft.xml <- getURL(url_ft) %>% fromJSON() %>%  htmlParse(asText = TRUE) 
  
  xmltop = xmlRoot(ft.xml) #gives content of root
  ft.df =ldply(xmlToList(xmltop[[1]]), data.frame) 

if (nrow(ft.df) > 2 ) # not all the products have data in financial times, 
{
  
  ft.df <- ft.df [-1,c(5,8,9,10,11)] # select the columns we need and remove the first row
  names(ft.df )<-c("date","Open","High","Low","Close") # rename de columms
  
  ft.df [ , c("type", "Name", "isin" , "LegalName", "OngoingCharge" , "category") ] <-  products [ i,] 
    
  df.return <-rbind( df.return ,ft.df )
 
   } else {   print( paste0( "the product", products[i,3], "does have any data in financial times API")) }

}

print( Sys.time() - start.time)

return(df.return)

}

dfe <-getFinancialtimesHistoricalData (ETFEI,2) # the second parameter is the number of months
dfi  <-getFinancialtimesHistoricalData (ITEI,2)


```



#data munging
Lets format the historical data from the financial times and store it, since i don't want to spend another 5 minutes more looking to the screen !
converting to numeric and date we will be able to use this dataset to do some simle technical analisis

```{r  munging,include=T} 

df <-rbind( dfe ,dfi )
df[,1] <- as.Date(df[,1], format="%a, %b %d, %Y") # date format
converToNumeric = function(x) { as.numeric(gsub(",", "", x, fixed = TRUE)) }
df[,2:5] = sapply(df[,2:5], converToNumeric) # numeric format

saveRDS(df, file.path(getwd(), "../input/etfs_itei.rds"))

```


# TTR lets use a little of thecnical analisys finding the  overbought and oversold etf or investmend funds 

```{r  aa, echo=T , message=F, warning=F}

rm(list = ls())

df <-readRDS("../input/etfs_itei.rds")

library(TTR) #  rsi() for calculating simple moving average

vector <- unique(df$isin)
dfa <- data.frame(stringsAsFactors=FALSE) 

for (i in vector)
{
  
e <- dplyr::filter(df,  isin == i)
  e <- e[order(as.Date(e$date, format="%Y-%m-%d")),]
  rsi <- RSI(e$Close, n=14)
  e$rsi <-rsi
  tail <- tail(e, 1)
   dfa <-rbind( dfa ,tail )

}

t <-tail (dfa[order(dfa$rsi),], 1)

h <-head (dfa[order(dfa$rsi),], 1)

```


# lets see if this is working w

```{r  eda, echo=T , message=F, warning=F}
library(plotly)


p1 <- plot_ly() %>% 
  add_trace(data=dplyr::filter(df,  isin == h$isin),
            x = ~date, y = ~Close, type="scatter", mode="lines", name = h$isin) 

  
print(p1)

p2 <- plot_ly() %>% 
    add_trace(data=dplyr::filter(df,  isin == t$isin),
            x = ~date, y = ~Close, type="scatter", mode = "lines" , name = t$isin) 
print(p2)
```


















