---
title: "fidelity new website"
output: html_document
---

```{r setup, include=FALSE}
rm(list = ls())

knitr::opts_chunk$set(echo = TRUE)
```

## Getting the products from fidelity

Recently Fidelity change their website offering new products, basically we have about 101 ETFs, 89 IETFs and about 2800 mutual funds

Below are the urls to gatter this information throught JSON and convert them to datasets, 
I got this urls using the web developer tools of mozilla, just take a look to the network console and you will see all the get post, put .. etc that the new 

What I really like about R, is the simpliclity of the code, look how we create three datasets with all the products of fidelity.



```{r cars}

library(jsonlite) 
library(XML)
library(RCurl)
library(stringr)
library(plyr)

url_ETFEI <- "http://lt.morningstar.com/api/rest.svc/9vehuxllxs/security/screener?page=1&pageSize=1000&sortOrder=LegalName%20asc&outputType=json&version=1&languageId=en-GB&currencyId=GBP&universeIds=ETEXG$XLON_3518|ETALL$$ALL_3518&securityDataPoints=SecId|Name|TenforeId|holdingTypeId|isin|sedol|QR_MonthDate|LegalName|Yield_M12|OngoingCharge|StarRatingM255|CustomCategoryId3Name|CollectedSRRI|QR_GBRReturnM12_5|QR_GBRReturnM12_4|QR_GBRReturnM12_3|QR_GBRReturnM12_2|QR_GBRReturnM12_1|CustomMinimumPurchaseAmount|GBRReturnM0|GBRReturnM12|GBRReturnM36|GBRReturnM60|GBRReturnM120&subUniverseId=ETFEI"

url_ITEI <-  "http://lt.morningstar.com/api/rest.svc/9vehuxllxs/security/screener?page=1&pageSize=1000&sortOrder=LegalName%20asc&outputType=json&version=1&languageId=en-GB&currencyId=GBP&universeIds=FCGBR%24%24ALL_3519&securityDataPoints=SecId%7CName%7CTenforeId%7CholdingTypeId%7Cisin%7Csedol%7CQR_MonthDate%7CLegalName%7CYield_M12%7CAnnualReportOngoingCharge%7CStarRatingM255%7CCustomCategoryId3Name%7CQR_GBRReturnM12_5%7CQR_GBRReturnM12_4%7CQR_GBRReturnM12_3%7CQR_GBRReturnM12_2%7CQR_GBRReturnM12_1%7CCustomMinimumPurchaseAmount%7CGBRReturnM0%7CGBRReturnM12%7CGBRReturnM36%7CGBRReturnM60%7CGBRReturnM120&filters=&term=&subUniverseId=ITEI"



library(dplyr)
ETFEI <- getURL(url_ETFEI) %>% fromJSON()  %>% as.data.frame
ITEI<- getURL(url_ITEI) %>% fromJSON()  %>% as.data.frame



#althougt the json gather many fields for this example we just use the below columns
ETFEI <- select (ETFEI,1,6,9,12,14,21)
ITEI <- select (ITEI,1,6,9,12,14,16)


names(ETFEI) <- c("type", "Name", "isin" , "LegalName", "OngoingCharge" , "category")
names(ITEI) <- c("type", "Name", "isin" , "LegalName", "OngoingCharge" , "category")


head(ETFEI)


```

## getting market data 

again lets use JSON to get market data this time from Financial times. 


```{r pressure, echo=FALSE}

library(lubridate)


getFTData<-function(products,months) {

df <- data.frame(stringsAsFactors=FALSE) 
start.time <- Sys.time()
end.date <-gsub("-", "/", Sys.Date())
start.date <-gsub("-", "/", Sys.Date()-months(months))

url_ft_base <- paste0("https://markets.ft.com/data/equities/ajax/get-historical-prices?startDate=", start.date, "&endDate=", end.date, "&symbol=" )
#for (i in 1:nrow(products)){
for (i in 1:5){
  
  url_ft = paste0(url_ft_base,products[i,3]) # third column is sthe isnn
  ft.xml <- getURL(url_ft) %>% fromJSON() %>%  htmlParse(asText = TRUE) 
  
  xmltop = xmlRoot(ft.xml) #gives content of root
  ft.df =ldply(xmlToList(xmltop[[1]]), data.frame) 

if (nrow(ft.df) > 2 ) # not all the products have data in financial times, 
{
  
  ft.df <- ft.df [-1,c(5,8,9,10,11)] # select the columns we need 
  names(ft.df )<-c("date","Open","High","Low","Close") # rename de columms
  ft.df [ , "fundsname"] <- products[i,2] #
  ft.df [ , "isin"] <-products[i,3]       #
  ft.df [ , "lname"] <-products[i,4]  
  ft.df [ , "charge"] <-products[i,5]  
  ft.df [ , "category"] <-products[i,6]  

  df <-rbind( df ,ft.df )
  } else {
    
    print( products[i,3])

}

}

end.time <- Sys.time()
time.taken <- end.time - start.time
print(time.taken)

return(df)

}

dfe <-getFTData (ETFEI,2) # the second parameter is the number of months
dfi  <-getFTData (ITEI,2)


```


#data munging
Lets format the historical data from the financial times and store it, since i don't want to spend another 5 minutes looking to the screen 

```{r  munging,include=FALSE} 

df <-rbind( dfe ,dfi )
df[,1] <- as.Date(df[,1], format="%a, %b %d, %Y") # date format
converToNumeric = function(x) { as.numeric(gsub(",", "", x, fixed = TRUE)) }
df[,2:5] = sapply(df[,2:5], converToNumeric) # numeric format

saveRDS(df, file.path(getwd(), "../input/etfs_itei.rds"))

```


# TTR lets use a little of thecnical analisys finding the  overbought and oversold etf or investmend funds 

```{r  aa, echo=FALSE} 

rm(list = ls())

df <-readRDS("../input/etfs_itei.rds")

library(TTR) #  rsi() for calculating simple moving average

vector <- unique(df$isin)
dfa <- data.frame(stringsAsFactors=FALSE) 

for (i in vector)
{
  
e <- dplyr::filter(df,  isin == i)
  e <- e[order(as.Date(e$date, format="%Y-%m-%d")),]
  rsi <- RSI(e$Close, n=14)
  e$rsi <-rsi
  tail <- tail(e, 1)
   dfa <-rbind( dfa ,tail )

}

t <-tail (dfa[order(dfa$rsi),], 1)

h <-head (dfa[order(dfa$rsi),], 1)

```


# lets see if this is working w

```{r  eda, echo=FALSE} 
library(plotly)


p1 <- plot_ly() %>% 
  add_trace(data=dplyr::filter(df,  isin == h$isin),
            x = ~date, y = ~Close, type="scatter", mode="lines", name = h$isin) 

  
print(p1)

p2 <- plot_ly() %>% 
    add_trace(data=dplyr::filter(df,  isin == t$isin),
            x = ~date, y = ~Close, type="scatter", mode = "lines" , name = t$isin) 
print(p2)
```


















