---
title: "fidelity new website"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Getting the products from fidelity

Recently Fidelity change their website offering new products, basically we have about 101 ETFs, 89 IETFs and about 2800 mutual funds

Below are the urls to gatter this information throught JSON and convert them to datasets, 
I got this urls using the web developer tools of mozilla, just take a look to the network console and you will see all the get post, put .. etc that the new 

What I really like about R, is the simpliclity of the code, look how we create three datasets with all the products of fidelity.



```{r cars}

rm(list = ls())
library(jsonlite) 
library(XML)
library(RCurl)
library(stringr)
library(plyr)

url_ETFEI <- "http://lt.morningstar.com/api/rest.svc/9vehuxllxs/security/screener?page=1&pageSize=1000&sortOrder=LegalName%20asc&outputType=json&version=1&languageId=en-GB&currencyId=GBP&universeIds=ETEXG$XLON_3518|ETALL$$ALL_3518&securityDataPoints=SecId|Name|TenforeId|holdingTypeId|isin|sedol|QR_MonthDate|LegalName|Yield_M12|OngoingCharge|StarRatingM255|CustomCategoryId3Name|CollectedSRRI|QR_GBRReturnM12_5|QR_GBRReturnM12_4|QR_GBRReturnM12_3|QR_GBRReturnM12_2|QR_GBRReturnM12_1|CustomMinimumPurchaseAmount|GBRReturnM0|GBRReturnM12|GBRReturnM36|GBRReturnM60|GBRReturnM120&subUniverseId=ETFEI"

url_ITEI <-  "http://lt.morningstar.com/api/rest.svc/9vehuxllxs/security/screener?page=1&pageSize=1000&sortOrder=LegalName%20asc&outputType=json&version=1&languageId=en-GB&currencyId=GBP&universeIds=FCGBR%24%24ALL_3519&securityDataPoints=SecId%7CName%7CTenforeId%7CholdingTypeId%7Cisin%7Csedol%7CQR_MonthDate%7CLegalName%7CYield_M12%7CAnnualReportOngoingCharge%7CStarRatingM255%7CCustomCategoryId3Name%7CQR_GBRReturnM12_5%7CQR_GBRReturnM12_4%7CQR_GBRReturnM12_3%7CQR_GBRReturnM12_2%7CQR_GBRReturnM12_1%7CCustomMinimumPurchaseAmount%7CGBRReturnM0%7CGBRReturnM12%7CGBRReturnM36%7CGBRReturnM60%7CGBRReturnM120&filters=&term=&subUniverseId=ITEI"

url_MFEI <-  "http://lt.morningstar.com/api/rest.svc/9vehuxllxs/security/screener?page=1&pageSize=3000&sortOrder=LegalName%20asc&outputType=json&version=1&languageId=en-GB&currencyId=GBP&universeIds=FOGBR%24%24ALL_3521&securityDataPoints=SecId%7CName%7CTenforeId%7CholdingTypeId%7Cisin%7Csedol%7CCustomAttributes1%7CCustomAttributes2%7CCustomExternalURL1%7CCustomExternalURL2%7CCustomExternalURL3%7CCustomIsClosed%7CCustomIsFavourite%7CCustomIsRecommended%7CQR_MonthDate%7CLegalName%7CCustomBuyFee%7CYield_M12%7COngoingCharge%7CCustomCategoryId3Name%7CStarRatingM255%7CQR_GBRReturnM12_5%7CQR_GBRReturnM12_4%7CQR_GBRReturnM12_3%7CQR_GBRReturnM12_2%7CQR_GBRReturnM12_1%7CCustomMinimumPurchaseAmount%7CCustomValue2%7CCustomAdditionalBuyFee%7CCustomSellFee%7CGBRReturnM0%7CGBRReturnM12%7CGBRReturnM36%7CGBRReturnM60%7CGBRReturnM120&filters=&term=&subUniverseId=MFEI"




library(dplyr)
ETFEI <- getURL(url_ETFEI) %>% fromJSON()  %>% as.data.frame
ITEI<- getURL(url_ITEI) %>% fromJSON()  %>% as.data.frame
MFEI <-getURL(url_MFEI) %>% fromJSON()  %>% as.data.frame




e <- select (ETFEI,1,6,9,12,14,21)
i <- select (ITEI,1,6,9,12,14,16)
m <- select (MFEI,1,6,9,15,17, 18)
head(m)

names(e) <- c("type", "Name", "isin" , "LegalName", "OngoingCharge" , "category")
names(i) <- c("type", "Name", "isin" , "LegalName", "OngoingCharge" , "category")
names(m)<- c("type", "Name", "isin" , "LegalName", "OngoingCharge" , "category")
ei <- rbind(e, i) 

all_products <- rbind (ei, m)

all_products <- all_products[order(-all_products$OngoingCharge),] 

all_products <- all_products[order(all_products$OngoingCharge),] 

```

## getting market data 

again lets use JSON to get market data this time from Financial times. 


```{r pressure, echo=FALSE}


getFTData<-function(products,nyear) {

df <- data.frame(stringsAsFactors=FALSE) 
start.time <- Sys.time()
end.date <-gsub("-", "/", Sys.Date())
start.date <-gsub("-", "/", Sys.Date()-years(nyear))

url_ft_base <- paste0("https://markets.ft.com/data/equities/ajax/get-historical-prices?startDate=", start.date, "&endDate=", end.date, "&symbol=" )
for (i in 1:nrow(e)){
  
  url_ft = paste0(url_ft_base,products[i,3]) # first column is sthe isnn
  ft.xml <- getURL(url_ft) %>% fromJSON() %>%  htmlParse(asText = TRUE) 
  xmltop = xmlRoot(ft.xml) #gives content of root
  ft.df =ldply(xmlToList(xmltop[[1]]), data.frame) 
  
  ft.df <- ft.df [-1,c(5,8,9,10,11)] # select the columns we need 
  
  names(ft.df )<-c("date","Open","High","Low","Close") # rename de columms
  ft.df [ , "fundsname"] <- products[i,2] #
  ft.df [ , "isin"] <-products[i,3]       #
  ft.df [ , "lname"] <-products[i,4]  
  ft.df [ , "category"] <-products[i,5]  
  df <-rbind( df ,ft.df )
}

end.time <- Sys.time()
time.taken <- end.time - start.time
print(time.taken)

return(df)

}

ft <-getFTData (e, 1)


```
```{r pressure, echo=FALSE}

rm(list = ls())
require(quantmod)



```


