---
title: "funds strategy backtest"
output: html_document
---


## funds strategy

```{r setup, echo=T, include=T, message=F, warning=F}


rm(list = ls())
library(jsonlite)  
library(XML)       
library(RCurl)     
library(stringr)   
library(plyr)      
library(dplyr)     
library(lubridate) 

```

© FIL Limited 2017
Investment types

Funds
Funds allow investors to pool their money together, which a fund manager will then invest on their behalf. The manager is responsible for choosing investments for the fund and tries to grow investors' money by spreading it over a range of company shares, bonds etc.
Unit trusts, offshore funds and open-ended investment companies (OEICs) can all be referred to generically as funds.

Exchange Traded Funds (ETFs)
Exchange traded funds are similar to the funds mentioned above except that they act like a share themselves, and are openly traded on a stock exchange such as the FTSE All Share.  Most ETFs aim to perform in line with a specific index or commodity (like gold) and often have low management fees.

Investment Trusts
These are funds registered as public limited companies (PLCs) with their own management teams and boards of directors. They can invest in public and private companies, have a specific number of shares in issue and are traded on a stock exchange themselves.

Shares
Companies issue shares to raise money they can use to grow. Buying a share means owning a small part of that company and its future fortunes. While you may not have any control over day-to-day operations, shareholders can profit from a company's growth.

Bonds and Gilts
Bonds are loans made to companies or governments with you as the lender. You receive regular interest payments throughout the life of the loan and the initial amount is returned to you at the end. Gilts are bonds issued by the British government.


```{r cars}


url_MFEI <-  "http://lt.morningstar.com/api/rest.svc/9vehuxllxs/security/screener?page=1&pageSize=3000&sortOrder=LegalName%20asc&outputType=json&version=1&languageId=en-GB&currencyId=GBP&universeIds=FOGBR%24%24ALL_3521&securityDataPoints=SecId%7CName%7CTenforeId%7CholdingTypeId%7Cisin%7Csedol%7CCustomAttributes1%7CCustomAttributes2%7CCustomExternalURL1%7CCustomExternalURL2%7CCustomExternalURL3%7CCustomIsClosed%7CCustomIsFavourite%7CCustomIsRecommended%7CQR_MonthDate%7CLegalName%7CCustomBuyFee%7CYield_M12%7COngoingCharge%7CCustomCategoryId3Name%7CStarRatingM255%7CQR_GBRReturnM12_5%7CQR_GBRReturnM12_4%7CQR_GBRReturnM12_3%7CQR_GBRReturnM12_2%7CQR_GBRReturnM12_1%7CCustomMinimumPurchaseAmount%7CCustomValue2%7CCustomAdditionalBuyFee%7CCustomSellFee%7CGBRReturnM0%7CGBRReturnM12%7CGBRReturnM36%7CGBRReturnM60%7CGBRReturnM120&filters=&term=&subUniverseId=MFEI"

MFEI <-getURL(url_MFEI) %>% fromJSON()  %>% as.data.frame

names(MFEI)

names(MFEI) <- gsub("rows.", "", names(MFEI)) # nicer names

fondos<-MFEI



```



# dta munging 
```{r pressure, echo=FALSE}

MFEIInc <- fondos  %>%  filter( !grepl("Acc",LegalName)) # we generate another dataset with just the incremental funds
MFEIAcc <- fondos  %>%  filter( !grepl("Inc",LegalName)) 


MFEIAccempty <-MFEIAcc %>% filter(  is.na(CustomCategoryId3Name)) 
MFEIIncempty <-MFEIInc %>% filter(  is.na(CustomCategoryId3Name)) 


MFEIInc %>% filter( grepl("Emer",LegalName, ignore.case = T))
MFEIInc %>% filter( grepl("Global",LegalName, ignore.case = T))





```


# lets gather sustainability information 





https://www.fundstrategy.co.uk/18-20-behind-numbers-uk-equity-funds-sustainability-lens-datapic/

IE00B4V6GM81


http://tools.morningstar.co.uk/api/rest.svc/t92wz0sj7c/security_details/F00000NGLO?viewId=sustainability&idtype=msid&responseViewFormat=json&languageId=en

F000001EZY

GB00B2PB2051

http://tools.morningstar.co.uk/api/rest.svc/t92wz0sj7c/security_details/F0000009KA?viewId=sustainability&idtype=msid&responseViewFormat=json&languageId=en

url_get <- 'http://tools.morningstar.co.uk/api/rest.svc/t92wz0sj7c/security_details/F00000NGLO?viewId=sustainability&idtype=msid&responseViewFormat=json&languageId=en'

```{r pressure, echo=FALSE}

 df.return <- data.frame(stringsAsFactors=FALSE) 



for (i in 1:25){
        
    
        url_get <- paste0("http://tools.morningstar.co.uk/api/rest.svc/t92wz0sj7c/security_details/", 
                     MFEIInc[i,5] ,  
                      '?viewId=sustainability&idtype=msid&responseViewFormat=json&languageId=en')

      ESG.data <-getURL(url_get) %>% fromJSON()  %>% as.data.frame


if (ncol(ESG.data) > 5 ) # these are the products with ESG information
{
     print( paste0( "the product ",  MFEIInc[i,5], " Does  have sustianibilita dadta ", i )) 
  

   
    df.return <-rbind( df.return ,ESG.data[1,5] , fill=T)
  
} else 
  {
    print( paste0( "the product ",  MFEIInc[i,5], " Does not have sustianibilita dadta" ,  i )) 
   }

}
ncol(df.return)

```


# how many we have by 
```{r pressure, echo=FALSE}
detach("package:plyr", unload=TRUE) 
aa <- MFEIInc %>% group_by( CustomCategoryId3Name) %>%   summarise(count= n())

pp <- plot_ly(aa, x = ~CustomCategoryId3Name, y = ~count,  
              type = 'scatter' , mode = 'markers', marker = list(size = 15))  %>% 

layout(title = "numbers of ratings by month",  showlegend = TRUE)
pp

```


## how are they doing by sector
```{r pressure, echo=FALSE}


temp <- MFEIInc %>% select(GBRReturnM0,GBRReturnM12,GBRReturnM36,isin,Name,CustomCategoryId3Name)

temp <- na.omit(temp) 

temp <- temp %>% group_by(CustomCategoryId3Name)%>% summarise(returnbycat=mean(GBRReturnM0))


plot_ly(temp, x = ~returnbycat, color = ~CustomCategoryId3Name, type = "box") %>%
  layout(title = "average score  for each type of rating",  showlegend = TRUE)

```
## how are they doing by sector
```{r pressure, echo=FALSE}

temp <- MFEIInc %>% select(GBRReturnM0,GBRReturnM12,GBRReturnM36,isin,Name,CustomCategoryId3Name)

temp <- na.omit(temp) 

temp <- temp %>% group_by(CustomCategoryId3Name)%>% summarise(returnbycat=mean(GBRReturnM0))




data <- diamonds %>% count(cut, clarity)

p <- ggplot2::diamonds %>% count(cut, clarity) %>%
  plot_ly(x = ~cut, y = ~n, color = ~clarity)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
p




```









































```{r pressure, echo=FALSE}
library(devtools)
install_github("ropensci/plotly")

 
p <- plot_ly(
  type = 'table',  # Specify type of plot as table
  
  # header is a list and every parameter shown below needs 
  # to be specified. Note that html tags can be used as well
  
  header = list(
    
    # First specify table headers
    # Note the enclosure within 'list'
    
    values = list(list('<b>EXPENSES</b>'),
                  list('<b>Q1</b>'),
                  list('<b>Q2</b>'), 
                  list('<b>Q3</b>'), 
                  list('<b>Q4</b>')),
    
    # Formatting 
    line = list(color = '#DFE8F3'),
    align = c('left','left','left','left','left'),
    font = list(color = c('#506784', '#506784', '#506784', '#506784', '#ab63fa'), size = 14)
  ),
  
  # Specify individual cells
  
  cells = list(
    
    # Now specify each cell content
    
    values = list(
      c('Salaries', 'Office', 'Merchandise', 'Legal', '<b>TOTAL</b>'),
      c(1200000, 20000, 80000, 2000, 12120000),
      c(1300000, 20000, 70000, 2000, 130902000),
      c(1300000, 20000, 120000, 2000, 131222000),
      c(1400000, 20000, 90000, 2000, 14102000)),
    
    # Formatting
    line = list(color = '#DFE8F3'),
    align = c('left', 'left', 'left', 'left', 'left'),
    font = list(color = c('#506784', '#506784', '#506784', '#506784', '#ab63fa'), size = 14),
    height = 48
    )) %>% 
  
  # Layout is needed to remove gridlines, axis zero lines and ticktext 
  # or else they will also show up
  
  layout(xaxis = list(zeroline = F, showgrid = F, showticklabels = F, domain = c(0, 0.5)),
         yaxis = list(zeroline = F, showgrid = F, showticklabels = F))
 
p
```