---
title: "top 50 fidelity funds"
author: "david soto"
date: "9/27/2017"
output: html_document
---

I've donwnloade this this little dataset from the fidelity webpage

```{r setup, include=FALSE}
rm(list = ls())
setwd("~/dataScience/blog/mfunds/")
library(data.table)
system("ls -l ./input")
selected_fidelity = fread('./input/top50.csv')
head (selected_fidelity)

```

## data scraping from financial times to get the historical data of the selected 50 of fidelity.


this process will take some minutes and will generate  a file , later on i will post how can we make another process for updating the file so we don't need to download all the historical data from the Financial times all days. 

```{r scraping,include=FALSE} 
library(jsonlite) 
library(XML)
library(RCurl)
library(stringr)
library(plyr)

library(lubridate)


end.date <-gsub("-", "/", Sys.Date())
start.date <-gsub("-", "/", Sys.Date()-years(3))



url_ft_base <- paste0("https://markets.ft.com/data/equities/ajax/get-historical-prices?startDate=", start.date, "&endDate=", end.date, "&symbol=" )
print(url_ft_base)
df <- data.frame(stringsAsFactors=FALSE) 

start.time <- Sys.time()

for (i in 1:50){
  
  url_ft = paste0(url_ft_base,selected_fidelity[i,2]) # second column is sthe isnn
  ft.xml <- getURL(url_ft) %>% fromJSON() %>%  htmlParse(asText = TRUE) 
  xmltop = xmlRoot(ft.xml) #gives content of root
  ft.df =ldply(xmlToList(xmltop[[1]]), data.frame) 
  
  ft.df <- ft.df [-1,c(5,8,9,10,11)] # select the columns we need 
  
  names(ft.df )<-c("date","Open","High","Low","Close") # rename de columms
  ft.df [ , "fundsname"] <- selected_fidelity[i,1] #
  ft.df [ , "isin"] <-selected_fidelity[i,2]       #
  ft.df [ , "AssetClass"] <-selected_fidelity[i,4]  
  ft.df [ , "Mcategory"] <-selected_fidelity[i,6]  
  df <-rbind( df ,ft.df )
}

end.time <- Sys.time()
time.taken <- end.time - start.time
time.taken

summary (df)

```

#data munging
Lets format the historical data from the financial times and store it, we will use this historical data for some analysis and backtesting in other post. 

```{r  munging,include=FALSE} 
df[,1] <- as.Date(df[,1], format="%a, %b %d, %Y") # date format
converToNumeric = function(x) { as.numeric(gsub(",", "", x, fixed = TRUE)) }
df[,2:5] = sapply(df[,2:5], converToNumeric) # numeric format

saveRDS(df, file.path(getwd(), "../input/selected50.rds"))

```

#Heat map

```{r  munging,include=FALSE} 
df[,1] <- as.Date(df[,1], format="%a, %b %d, %Y") # date format
converToNumeric = function(x) { as.numeric(gsub(",", "", x, fixed = TRUE)) }
df[,2:5] = sapply(df[,2:5], converToNumeric) # numeric format

saveRDS(df, file.path(getwd(), "../input/selected50.rds"))

```

http://past.rinfinance.com/agenda/2010/JoshUlrich.pdf

```{r  munging,include=FALSE} 
rm(list = ls())
setwd("D:\\repos\\blog\\mfunds\\")
selected <- readRDS("../input/selected50.rds") 

library(TTR) #  rsi() for calculating simple moving average
GB00BYSYZL73 <- dplyr::filter(selected,  isin == "GB00BYSYZL73")

rsi <- RSI(GB00BYSYZL73$Close, n=14)

GB00BYSYZL73$rsi  <-rsi

```


```{r  munging,include=FALSE} 
df
setwd("D:\\repos\\blog\\mfunds\\")
selected <- readRDS("../input/selected50.rds") 
library(TTR) #  rsi() for calculating simple moving average


vector <- unique(selected$isin)
df <- data.frame(stringsAsFactors=FALSE) 

for (i in vector)
{
  
data <- dplyr::filter(selected,  isin == i)
  data <- data[order(as.Date(data$date, format="%Y-%m-%d")),]
  rsi <- RSI(GBxx$Close, n=14)
  GBxx$rsi <-rsi
  tail <- tail(GBxx, 1)
   df <-rbind( df ,tail )

}




```

